The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-11-12 paper/model_3.tex
paper JNW comments round 1

In this model, as in the previous one, all single and primary stars have 
identical properties.
Only the secondaries have masses, radii, and luminosities that vary between 
systems: $M\propto R \propto L^{1/\alpha}$.
The radii of planets are assigned independently of any host system
property, and are sampled from an intrinsic radius distribution, which we take 
as
\begin{align}
p_r(r)
&\propto
\left.
\begin{cases}
r^\delta & \text{for } r\geq 2r_\oplus \\
{\rm constant} & \text{for } r\leq2r_\oplus.
\end{cases}
\right.
\label{eq:model3_radius_distribution}
\end{align}
Following Howard et al. (2012)'s measurement, we take $\delta = -2.92$.
Our ``nominal model'' remains the same: the binary fraction is 0.44, 
$\alpha=3.5$, $\beta=\gamma=0$.
We take $\Lambda_i$, the occurrence rate integrated over all possible phase 
space for the $i^{\rm th}$ system type, to be equal for singles, primaries, 
and secondaries.

For this model, we forgo analytic development and focus only on numerics 
(Sec.~\ref{sec:numerical_methods}).
The nominal results are shown in Fig.~\ref{fig:errcases_model_3_log}.
For the assumed planetary and stellar distributions, the inferred rate is 
underestimated over all radii.

@@

However, this result only applies under the assumption that $\Lambda_0 = 
\Lambda_1 = \Lambda_2$.
If hot Jupiters are less common around lower mass stars, it would be more 
sensible to consider $\Lambda_2<\Lambda_0$, while letting single stars and 
primaries host planets at the same rate.
Therefore in Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues} we let 
$\Lambda_2$ vary, and show the resulting inferred and true hot Jupiter 
($r>8r_\oplus$) rates.
The result is that the inferred rate is nearly independent of 
$\Lambda_2$~--~this is because most ($<1/10$) secondaries are not searchable, 
and so their completeness fraction is much smaller than that of primaries or 
single stars.
This means far fewer detected hot Jupiters orbit secondaries, and so they 
hardly affect the inferred rate.
While the ``true rate'' across the entire population is highly dependent on 
$\Lambda_2$, as one would expect from Eq.~\ref{eq:occ_rate}, the rate around 
singles and primaries (green line) is independent of that around secondaries.
Assuming that RV surveys are measuring the true rate around single stars (or 
primaries), this suggests that binarity might contributes to the 
HJ rate discrepancy at the $\sim 0.2\%$ level, independent of the HJ rate 
around secondaries.

@@

Our model does not explicitly include the rate density's period-dependence, 
because stellar binarity does not appreciably bias the period-dependence of 
occurrence rates measured by transit surveys\footnote{
    Note that stellar binarity does bias the {\it intrinsic} planet 
    occurrence as a function of planetary and binary periods. This is expected 
    from dynamical stability limits in $\geq$3 body systems, and has been 
    observationally confirmed (theory by Holman \& Wiegert 1999, and others 
    including Gongjie; confirmation from Wang et al 2014a, 2014b, Kraus et al 
    2014). 
    However our statement is that inferred rates as a function of planet     
    period should be negligibly affected by this, given the geometric bias 
    against long-period transit detections, and the fact that the period 
    distribution of solar-type binaries peaks at $\approx 100\,{\rm years}$ 
    (Raghavan et al 2010, Fig.~13).
}.
Instead, it allows us to evaluate the difference in the apparent and true rate 
as a function of radius 
(Fig.~\ref{fig:errcases_model_3_log}).
At Earth's radius, the result is that the inferred rate is $0.84\times$ the 
true rate around single stars, assuming that the $\Lambda_i$'s are equal.
Similar to the above case of the hot Jupiters, if we vary the true $\Lambda_2$ 
while keeping $\Lambda_0 = \Lambda_1$, the ratio of the inferred to true rate 
around single stars hardly 
changes; $(\Lambda_{\rm inferred}/\Lambda_1)_{r=r_\oplus} \approx 0.135$, to 
within a few percent, independent of $\Lambda_2$ (shown in 
Fig.~\ref{fig:earth_inputrate_vs_etaearthratevalues}).
The ratio of the inferred to the true rate, $(\Lambda_{\rm 
inferred}/\Lambda)_{r=r_\oplus}$ varies substantially, but by at most $50\%$ 
in the (unrealistic) limiting case that secondaries do not host planets.

>>>>

In this model, as in the previous one, all single and primary stars have 
identical properties.
Only the secondaries have masses, radii, and luminosities that vary between 
systems: $M\propto R \propto L^{1/\alpha}$.
The radii of planets are assigned independently of any host system
property, and are sampled from an intrinsic radius distribution, which we take 
as
\begin{align}
p_r(r)
&\propto
\left.
\begin{cases}
r^\delta & \text{for } r\geq 2r_\oplus \\
{\rm constant} & \text{for } r\leq2r_\oplus.
\end{cases}
\right.
\label{eq:model3_radius_distribution}
\end{align}
Following Howard et al. (2012)'s measurement, we take $\delta = -2.92$.
Our ``nominal model'' remains the same: the binary fraction is 0.44, 
$\alpha=3.5$, $\beta=\gamma=0$.
We take $Z_i$, the occurrence rate integrated over all planet radii for the 
$i^{\rm th}$ system type, to be equal for singles, primaries, 
and secondaries.

For this model, we forgo analytic development and focus only on numerics.
The occurrence rates are shown as a function of planet radius in 
Fig.~\ref{fig:errcases_model_3_log}.
For the assumed planetary and stellar distributions, the inferred rate is 
underestimated over all radii.

\begin{figure}[!tb]
    \centering
    \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_logs_model_3.pdf}
    \caption{
        Inferred planet occurrence rates as a function of planet radius in 
        Model 
        \#3.
        This model has fixed primaries and single stars, but varying 
        secondaries.
        The true planet radius distribution is a power law with exponent 
        $-2.92$ 
        above $2R_\oplus$, below which it is uniform (e.g., Howard et al., 
        2012).
    }
    \label{fig:errcases_model_3_log}
\end{figure}

@@

However, this result only applies under the assumption that $Z_0 = 
Z_1 = Z_2$.
If hot Jupiters are less common around lower mass stars, it would be more 
sensible to consider $Z_2<Z_0$, while letting single stars and 
primaries host planets at the same rate.
Therefore in Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues} we let 
$Z_2$ vary, and show the resulting inferred and true hot Jupiter 
($r>8r_\oplus$) rates.
The result is that the inferred rate is nearly independent of 
$Z_2$~--~this is because most ($<1/10$) secondaries are not searchable, 
and so their completeness fraction is much smaller than that of primaries or 
single stars.
This means far fewer detected hot Jupiters orbit secondaries, and so they 
hardly affect the inferred rate.
While the ``true rate'' across the entire population is linearly dependent on 
$Z_2$, the rate around 
singles and primaries (green line) is independent of that around secondaries.
Assuming that RV surveys are measuring the true rate around single stars (or 
primaries), this suggests that binarity might contributes to the 
HJ rate discrepancy at the $\sim 0.2\%$ level, independent of the HJ rate 
around secondaries.

\begin{figure}[!tb]
    \centering
    \includegraphics[width=.6\textwidth]{figures/HJ_correction_inputrate_vs_HJratevalues.pdf}
    \caption{
        $X_i$ is the occurrence rate integrated over all possible phase 
        space for the $i^{\rm th}$ system type. $Z_2/Z_0=1$ 
        corresponds to an equal number of planets per secondary as per single 
        star;
        $Z_2/Z_0=0$ corresponds to secondaries not having any 
        planets.
        In our Model \#3, though the true HJ occurrence rate 
        is highly dependent on $Z_2$, 
        the inferred rate hardly depends on whether secondaries have HJs.
        This means that the ``correction factor'' between the inferred rate 
        and the true rate around single stars is underestimated by a 
        multiplicative 
        factor of $\approx1.3$, independent of the HJ rate around secondaries.
        The ``HJ rate'' is the summed rate from     
        Fig.~\ref{fig:errcases_model_3_log} above $8r_\oplus$.
    }
    \label{fig:HJ_correction_inputrate_vs_HJratevalues}
\end{figure}

@@

Our model does not explicitly include the rate density's period-dependence, 
because stellar binarity does not appreciably bias the period-dependence of 
occurrence rates measured by transit surveys\footnote{
    Note that stellar binarity does bias the {\it intrinsic} planet 
    occurrence as a function of planetary and binary periods. This is expected 
    from dynamical stability limits in $\geq$3 body systems, and has been 
    observationally confirmed (theory by Holman \& Wiegert 1999, and others 
    including Gongjie; confirmation from Wang et al 2014a, 2014b, Kraus et al 
    2014). 
    However our statement is that inferred rates as a function of planet     
    period should be negligibly affected by this, given the geometric bias 
    against long-period transit detections, and the fact that the period 
    distribution of solar-type binaries peaks at $\approx 100\,{\rm years}$ 
    (Raghavan et al 2010, Fig.~13).
}.
Instead, it allows us to evaluate the difference in the apparent and true rate 
as a function of radius 
(Fig.~\ref{fig:errcases_model_3_log}).
At Earth's radius, the result is that the inferred rate is $0.84\times$ the 
true rate around single stars, assuming that the $Z_i$'s are equal.
Similar to the above case of the hot Jupiters, if we vary the true $Z_2$ 
while keeping $Z_0 = Z_1$, the ratio of the inferred to true rate 
around single stars hardly 
changes by only a few percent (shown in 
Fig.~\ref{fig:earth_inputrate_vs_etaearthratevalues}).
The ratio of the inferred to the true rate, $(\Lambda_{\rm 
inferred}/\Lambda)_{r=r_\oplus}$ varies substantially, but by at most $50\%$ 
in the (unrealistic) limiting case that secondaries do not host planets.

\begin{figure}[!tb]
    \centering
    \includegraphics[width=.6\textwidth]{figures/earth_inputrate_vs_etaearthratevalues.pdf}
    \caption{
        Same as Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues}, but 
        for Earth-sized planets.
        The absolute values given on the $y$-axis found by summing the rate 
        from Fig.~\ref{fig:errcases_model_3_log} for planetary radii from 
        $0.5$ to $1.5r_\oplus$ (this is a toy model, and they do not reflect 
        an actual determination of $\eta_\oplus$).
        The relative values show that the inferred rate for Earths is roughly 
        independent of the occurrence rate (integrated over all radii) around 
        secondaries.
        However, it is systematically lower than the true rate around single 
        and primary stars, by $\approx 20\%$.
    }
    \label{fig:earth_inputrate_vs_etaearthratevalues}
\end{figure}

### 2017-11-12 paper/simplest_effects.tex
paper JNW comments round 1

\section{Idealized Models of Transit Surveys}

@@

We return to our group of binarity-ignoring astronomers. They do 
not know the true planet population~--~they would like to discover it!
In their signal-to-noise limited transit survey, they select stars 
that they think can yield transit detections.
Since the noise is Poissonian, they assume
\begin{equation}
\frac{{\rm signal}}{{\rm noise}}
\propto \frac{(r/R)^2}{F^{-1/2}}
\propto F^{1/2}
\propto L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm incorrectly\ assumed})
\end{equation}
for $R$ the (constant) stellar radius, $F$ the photon flux, $L_{\rm sys}$ the 
luminosity of a system, and $d$ its distance from us.
At fixed planet radius, semimajor axis, stellar radius, and stellar luminosity,
a constant signal-to-noise floor yields a maximum detectable 
distance (Pepper et al 2003, Pepper and Gaudi 2005).
The maximum distance out to which our binarity-ignoring astronomers 
select stars, $d_{\rm sel}$, thus scales as $L_{\rm sys}^{1/2}$.

The single stars have luminosity $L_1$, and the twin binaries have luminosity 
$2L_1$.
Thus the twin binaries are selected out to a distance $\sqrt{2}$ times 
that of single stars.
This is a bad move; in reality the transit signal for any planet in a 
twin binary will be diluted by a factor of two:
\begin{equation}
\frac{{\rm signal}}{{\rm noise}}
\propto \frac{\mathcal{D} (r/R)^2}{F^{-1/2}}
\propto \mathcal{D} F^{1/2}
\propto \mathcal{D} L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm true})
\end{equation}
where the dilution is $\mathcal{D} \equiv L_{\rm host}/L_{\rm sys}$, for 
$L_{\rm host}$ the the planet host's luminosity.
This means that the actual maximum searchable distance for binaries is 
$1/\sqrt{2}\times$ that of single stars.
The situation is illustrated in Fig.~\ref{fig:model_1_volumes}: only one in 
eight selected stars in binaries are truly searchable.

\paragraph{What do the observers ignoring binarity infer?} 
The binarity-ignoring observers assume that every point on the sky with flux 
above some minimum are searchable.
They measure a detected planet rate density, and infer an apparent rate 
density by correcting for $p_{\rm tra}$.
The apparent rate density is
\begin{equation}
\Gamma_a(r) = 
\delta(r_p) Z_0 \frac{N_0}{N_0+N_1}  +
\delta\left(\frac{r_p}{\sqrt{2}}\right) 
(Z_1 p_{{\rm det},1} + Z_2 p_{{\rm det},2}) \frac{N_1}{N_0+N_1},
\label{eq:model_1_apparent_rate_density}
\end{equation}
where $p_{{\rm det},1}$ ($p_{{\rm det},2}$) is the probability that a selected 
primary (secondary) is searchable.
For this example, $p_{{\rm det},1}=p_{{\rm det},2}=1/8$.

The true rate density (Eq.~\ref{eq:model_1_rate_density}) and the
apparent rate density (Eq.~\ref{eq:model_1_apparent_rate_density})
differ in that
\begin{enumerate}
\item The total number of selected stars, $N_{\rm tot} = N_0+N_1+N_2$, was 
miscounted.
%
\item The detection efficiency was incorrectly assumed to be $1$ for all 
selected stars. In reality, only one in eight binaries were searchable.
%
\item The inferred radii in binary systems are all $\sqrt{2}$ too small.
\end{enumerate}

We show the resulting occurrence rates over bins in planet radius in 
Fig.~\ref{fig:errcases_model_1}.

%NOTE: YOU CAN BUTCHER THE FUCK OUT OF THIS SECTION. JNW WANTS EACH CASE TO BE 
%EXPLAINED, INDIVIDUALLY. DROP ALL THE "i" SUBSCRIPTS B/C THEY ARE APPARENTLY 
%CONFUSING.

To express the rate density of detected planets, $\hat{\Gamma} = \sum 
Q_i\Gamma_i$, we need the detection efficiencies for each system type, which 
are products of the geometric and selection probabilities:
\begin{align}
Q_i(\vec{x}) &= Q_{g,i}(\vec{x}) Q_{c,i}(\vec{x}),\quad {\rm where}\ 
\vec{x}=(r,R,a).
\label{eq:general_detection_efficiency}
\end{align}
Similar to Pepper et al. (2003), but in a new context, we take $Q_c$ as the 
ratio of the number of stars that were searchable to the number of stars that 
were selected.
Assuming a homogeneous distribution of stars, this gives
\begin{equation}
Q_{c,i}(\vec{x}) = \left(
\frac{d_{{\rm det},i}(\vec{x})}{d_{\rm sel}(\vec{x})}
\right)^3,
\end{equation}
for $d_{\rm sel}$ the maximum distance to which surveyed stars are selected, 
and $d_{{\rm det},i}$ the maximum distance to which planets can actually be 
detected about the $i^{\rm th}$ system type.
Note that $d_{\rm sel} \geq d_{{\rm det},i}$.
In a signal-to-noise limited transit survey in which the observer does not 
know which stars are binaries, 
\begin{equation}
d_{\rm sel} \propto (r/R)^2 (L_{\rm sys} T_{\rm dur} A N_{\rm tra})^{1/2},
\end{equation}
for $L_{\rm sys}=L_1(1+\ell)$ the system luminosity, $T_{\rm dur}$ the 
transit duration, $A$ the detector area, and $N_{\rm tra}$ 
the number of observed transits.
However,
\begin{equation}
d_{{\rm det},i} \propto \mathcal{D}_i(r/R)^2 (L_{\rm sys} T_{\rm dur} A N_{\rm 
    tra})^{1/2},
\label{eq:d_det_i}
\end{equation}
for the dilution $\mathcal{D}_i$ given by
\begin{align}
\mathcal{D}_i
&=
\left.
\begin{cases}
1 & \text{for } i=0,\ {\rm single} \\
L_1 / L_{\rm sys} = (1+\ell)^{-1}, & \text{for } i=1,\ {\rm primary} \\
\ell L_1 / L_{\rm sys} = (1 + \ell^{-1})^{-1}, & 
\text{for } i=2,\ {\rm secondary},
\end{cases}
\right.
\label{eq:dilution}
\end{align}
where the light ratio $\ell$ of a given binary is defined as the ratio of 
the luminosity of the secondary to the primary.

The maximum detectable distance to single stars is assumed to be known, and so 
$d_{{\rm sel},0} = d_{{\rm det},0}$.
This means our naive astronomer assumes the fraction of their selected stars 
which are searchable is 1 (this is their ``assumed completeness'').
For binary systems there is a necessary incompleteness, and combining 
Eqs.~\ref{eq:general_detection_efficiency} through~\ref{eq:dilution} yields
\begin{align}
Q_0 &= Q_{g,0}Q_{c,0} = Q_{g,0} \label{eq:detection_efficiency_0}\\
Q_1 &= Q_{g,1}Q_{c,1} = Q_{g,0} (1+q^\alpha)^{-3} \\
Q_2 &= Q_{g,2}Q_{c,2} = Q_{g,0} q^{2/3} (1+q^{-\alpha})^{-3} q^{-5}, 
\label{eq:detection_efficiency_2}
\end{align}
for $Q_{g,0}=R/a$, the transit probability in single star systems.
In Eq.~\ref{eq:detection_efficiency_2}, we have assumed a stellar 
mass-luminosity-radius relation: $R\propto M \propto L^{1/\alpha}$.
The geometric transit probability is $Q_{g,2} = Q_{g,0}q^{2/3}$, and the 
completeness is the latter term of Eq.~\ref{eq:detection_efficiency_2}.
For $q=1$, the $q^{2/3}$ and $q^{-5}$ evaluate to unity, but they will later 
become relevant.

Summarizing, we have written the rate density for each system type
(Eq.~\ref{eq:model1_occ_rate_density}) and the detection efficiency for each 
system type 
(Eq.~\ref{eq:detection_efficiency_0}-\ref{eq:detection_efficiency_2}),
and so have fully specified the rate density of detected planets, 
in addition to the true rate density.

@@

Define a rate density correction factor, $X_\Gamma$, as the ratio of the 
apparent to true rate densities:
\begin{equation}
X_\Gamma \equiv \frac{\Gamma_a}{\Gamma}.
\end{equation}
This factor can be a function of whatever parameters $\Gamma_a$ and $\Gamma$ 
depend on; in this study, the planet radius is most relevant.
For the twin-binaries model,
\begin{equation}
X_\Gamma(r)
=
\frac{w_a \Lambda_0\delta^3(r_p) + 
    w_b(\Lambda_1 Q_{c,1} + \Lambda_2 Q_{c,2}) \delta^3(r_p/\sqrt{2})  }
{(w_0\Lambda_0 + w_1\Lambda_1 + w_2\Lambda_2)\delta^3(r_p)}
\label{eq:model1_correction}
\end{equation}
where $\delta^3(r_p)$ is shorthand for $\delta^3(r-r_p,R-R_\star,a-a_p)$.

If we take the rates $\Lambda_i$ to be equal, applying the definitions of 
the weights gives a rate density correction factor at $r=r_p$ of
$X_\Gamma(r_p) = (1+\mu)^{-1}$, where 
\begin{align}
\mu \equiv \frac{N_1}{N_0} &=
\frac{n_b}{n_s} \left(\frac{d_{\rm sel,b}}{d_{\rm sel,s}}\right)^3 = 
\frac{{\rm BF}}{1-{\rm BF}} (1+\ell)^{3/2},
\label{eq:mu_definition}
\end{align}
for $n_b$ and $n_s$ the number density of binaries and singles in a 
volume limited sample.
Using Raghavan et al. (2010)'s $0.7-1.3M_\odot$ multiplicity fraction as our 
binary fraction\footnote{
    The binary fraction is the fraction of systems in a volume-limited sample 
    that 
    are binary. It is equivalent to the multiplicity fraction if there are no 
    triple, quadruple, or higher order multiples. In that case, ${\rm BF} = 
    n_b / 
    (n_s+n_b)$.
}, we set ${\rm BF}=0.44$.
The resulting correction to the rate density is $X_\Gamma(r_p) \approx 0.31$. 
The correction at $r_p/\sqrt{2}$ is infinite.
The numerical realization of this model agrees with these analytic values, and 
its output is shown in Fig~\ref{fig:errcases_model_1}.
%beta = 2.2223355980148636
If instead we assume that $\Lambda_0 = \Lambda_1$, but that $\Lambda_2=0$, we 
find 
$X_\Gamma(r_p) = (1+2\mu)/(1+\mu)^2$.
Taking the same binary fraction, this evaluates to $X_\Gamma(r_p)\approx 0.53$.
Since the correction to the rate is equal to that of rate density, at 
$r=r_p$, the occurrence rate is underestimated by a factor of roughly 2 to 3.

%Note that a correction to the inferred rate, $X_\Lambda$, can be 
%defined analogously:
%\begin{equation}
%X_\Lambda \equiv \frac{\Lambda_a}{\Lambda}.
%\end{equation}
%For this twin binary model, the correction to the rate is the same as that to 
%the rate density.

>>>>

@@

We return to our group of binarity-ignoring astronomers. They do 
not know the true rate density~--~they would like to discover it!
In their signal-to-noise limited transit survey, they select stars 
that they think can yield transit detections.
Since the noise is Poissonian, they assume
\begin{equation}
\frac{{\rm signal}}{{\rm noise}}
\propto \frac{(r/R)^2}{F^{-1/2}}
\propto F^{1/2}
\propto L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm incorrectly\ assumed})
\end{equation}
for $R$ the constant stellar radius, $F$ the photon flux, $L_{\rm sys}$ the 
luminosity of a system, and $d$ its distance from us.
At fixed planet radius, semimajor axis, stellar radius, and stellar luminosity,
a constant signal-to-noise floor yields a maximum detectable 
distance (Pepper et al 2003, Pepper and Gaudi 2005).
The maximum distance out to which our binarity-ignoring astronomers 
select stars, $d_{\rm sel}$, thus scales as $L_{\rm sys}^{1/2}$.

The single stars have luminosity $L_1$, and the twin binaries have luminosity 
$2L_1$.
Thus the twin binaries are selected out to a distance $\sqrt{2}$ times 
that of single stars.
This is a bad move, because the transit signal for any planet in a 
twin binary will be diluted by a factor of two:
\begin{equation}
\frac{{\rm signal}}{{\rm noise}}
\propto \frac{\mathcal{D} (r/R)^2}{F^{-1/2}}
\propto \mathcal{D} F^{1/2}
\propto \mathcal{D} L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm true})
\end{equation}
where the dilution is $\mathcal{D} \equiv L_{\rm host}/L_{\rm sys}$, for 
$L_{\rm host}$ the the planet host's luminosity.
This means that the actual maximum searchable distance for binaries, $d_{\rm 
det}$, is $1/\sqrt{2}$ times that of single stars.
The situation is illustrated in Fig.~\ref{fig:model_1_volumes}: only one in 
eight selected stars in binaries are truly searchable.

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=0.6\textwidth]{figures/visualize_volumes.pdf}
    \end{center}
    \caption{
        Cartoon of the different selected and searchable volumes for single 
        stars (left column), and twin binaries (right column).
        This model (\#1) assumes all stars have equal mass and luminosity.
        Since the observer does not recognize the brighter binaries, they 
        select 
        them out to a larger distance, $\sqrt{2}\times$ that of single stars.
        However, dilution causes the twin binaries to only be searchable in 
        one 
        eighth of their selected volume.
    }
    \label{fig:model_1_volumes}
\end{figure}

\paragraph{What do the observers ignoring binarity infer?} 
The binarity-ignoring observers assume that all points on the sky with flux 
above some minimum are searchable.
They measure a detected planet rate density, and infer a rate 
density by correcting for the transit probability.
As a function of apparent radius, the apparent rate density is
\begin{equation}
\Gamma_a(r_a) = 
\delta(r_p) Z_0 \frac{N_0}{N_0+N_1}  +
\delta\left(\frac{r_p}{\sqrt{2}}\right) 
(Z_1 p_{{\rm det},1} + Z_2 p_{{\rm det},2}) \frac{N_1}{N_0+N_1},
\label{eq:model_1_apparent_rate_density}
\end{equation}
where $p_{{\rm det},1}$ ($p_{{\rm det},2}$) is the probability that a selected 
primary (secondary) is searchable.
In this example, $p_{{\rm det},1}=p_{{\rm det},2}=1/8$; the detection 
efficiency is the ratio of the searchable to selected volumes.

The true rate density (Eq.~\ref{eq:model_1_rate_density}) and the
apparent rate density (Eq.~\ref{eq:model_1_apparent_rate_density})
differ in that
\begin{enumerate}
\item The total number of selected stars, $N_{\rm tot} = N_0+N_1+N_2$, was 
miscounted.
%
\item The detection efficiency was incorrectly assumed to be $1$ for all 
selected stars. In reality, only one in eight binaries were searchable.
%
\item The inferred radii in binary systems are all $\sqrt{2}$ too small.
\end{enumerate}
By making an assumption about the true number of planets per single, primary, 
and secondary star ($Z_0,Z_1,$ and $Z_2$), we can assess the severity of 
these errors.
Taking $Z_0=Z_1=Z_2$, we plot the resulting occurrence rates over bins 
in planet radius in Fig.~\ref{fig:errcases_model_1}.
Though it is impossible for an observer to isolate any one of the above 
errors without also addressing the others, mathematically it is simply a 
matter of modifying the appropriate terms in 
Eq.~\ref{eq:model_1_apparent_rate_density}.
The resulting rates are also shown in 
Fig.~\ref{fig:errcases_model_1}, and demonstrate how each 
error individually affects the overall inferred rate.

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        Inferred planet occurrence rates over $0.01r_\oplus$ bins in planet 
        radius,
        for Model \#1.
        This model has fixed stars, fixed planets, and twin binaries.
        If the true planet radius is $r_p$, all planets 
        detected in binaries will have apparent radii $r_a = r_p/\sqrt{2}$.
        To illustrate the individual biases, we 
        separated them:
        ``only wrong $N_\star$'' means the only error is an incorrectly 
        assumed 
        number of selected stars;
        ``only wrong $Q$'' means the only error is an incorrectly assumed 
        detection efficiency (including both miscalculated transit 
        probabilities 
        and 
        fraction of selected stars that are searchable);
        ``only wrong $r_a$'' means the only error is misinterpretation of 
        planetary radii, due to both transit depth dilution and also wrongly 
        assumed host star radii.
    }
    \label{fig:errcases_model_1}
\end{figure}

@@

We define a rate density correction factor, $X_\Gamma$, as the ratio of the 
apparent to true rate densities:
\begin{equation}
X_\Gamma \equiv \frac{\Gamma_a}{\Gamma}.
\end{equation}
This correction factor can be a function of whatever parameters $\Gamma_a$ and 
$\Gamma$ depend on; in this study, the planet radius is most relevant.

Still assuming that the number of planets per single, primary, and 
secondary star are equal ($Z_0=Z_1=Z_2$), we find a rate density correction 
factor at the true planet radius of
\begin{equation}
X_\Gamma(r_p) = (1+\mu)^{-1},
\label{eq:Z_eq_model_1_correction}
\end{equation}
where 
\begin{align}
\mu \equiv \frac{N_1}{N_0} &=
\frac{n_b}{n_s} \left(\frac{d_{\rm sel,b}}{d_{\rm sel,s}}\right)^3 = 
\frac{{\rm BF}}{1-{\rm BF}} (1+\ell)^{3/2}.
\label{eq:mu_definition}
\end{align}
In Eq.~\ref{eq:mu_definition}, $n_b$ and $n_s$ are the number density of 
binaries and singles in a volume limited sample, and the maximum selected 
distance for binary and single systems are $d_{\rm sel,b}$ and $d_{\rm sel,s}$.
The light ratio $\ell$ is defined relative to the primary, so that
$L_{\rm sys} = L_1(1+\ell)$.
The binary fraction in a volume limited sample is ``{\rm BF}''.
For instance, Raghavan et al., (2010) found a multiplicity fraction\footnote{
    The binary fraction is the fraction of systems in a volume-limited sample 
    that are binary. It is equivalent to the multiplicity fraction if there 
    are no triple, quadruple, or higher order multiples. In that case, ${\rm 
    BF} = n_b / (n_s+n_b)$.
}
for primaries with masses $0.7-1.3M_\odot$ of 0.44. 
``Twin binaries'' are perhaps 10-20\% of the binaries in a volume-limited 
sample, depending on how ``twin'' is defined.
Thus a representative twin binary fraction to use in
Eq.~\ref{eq:Z_eq_model_1_correction} would be ${\rm BF}\approx 
0.05$-$0.1$. This yields a rate density correction $X_\Gamma(r_p)$ of 0.79 if 
${\rm BF}=0.1$, and 0.88 if ${\rm BF}=0.05$.
Rephrasing the result, the apparent rate would be half the true rate 
if the twin binary fraction were $(2^{3/2}+1)^{-1}\approx 0.26$.
Fortunately, in most contexts it is not that high.

An alternative assumption is that secondaries do not host planets. In this 
case, $Z_0=Z_1$, and $Z_2=0$. The correction to the rate density at the true 
planet radius becomes
\begin{equation}
X_\Gamma(r_p) = (1+2\mu)/(1+\mu)^2.
\end{equation}
This evaluates to 0.95 if ${\rm BF}=0.1$, and 0.99 if ${\rm BF}=0.05$.
While it is hard to justify the assumption that secondaries are planet-less, 
it is worth noting that $\Gamma_a/\Gamma$ is sensitive to the relative number 
of planets per single, primary, and secondary.
